An Open Repository of Real-Time COVID-19 Indicators

### 2021-06-21 indicators/paper/supplement.Rmd
Rename HSP-HOSP -> HSP-Hosp in indicators supplement

```{r hospitalization_time_trends_national, fig.cap="National trends, from April 2020 to April 2021, of HHS confirmed COVID-19 hospital admissions, plus three other signals in the COVIDcast API. Here, the HHS data has been limited to values from 2020-08-01 onward due to changes in reporting behavior, and processed into a 7-day trailing average rate per 100,000 resident population using Census Bureau estimates for 2019. HSP-HOSP is the percentage of new hospital admissions with COVID-associated diagnoses, based on claims data from health system partners, smoothed in time and adjusted for systematic day-of-week effects. Auxiliary signals have been scaled to have the same maximum value as the HHS data."}
start_day = "2020-04-15"
end_day = "2021-04-15"
as_of_day = "2021-06-01"

HOSP_SOURCES <-
  c("hhs", "hospital-admissions", "jhu-csse", "chng")
HOSP_SIGNALS <-
  c("confirmed_admissions_covid_1d",
    "smoothed_adj_covid19_from_claims",
    "confirmed_7dav_incidence_prop",
    "smoothed_adj_outpatient_covid")
hosp_names = c(
  "Hospitalizations", "HSP-HOSP",
  "Cases", "CHNG-COVID"
)
hosp_signal_has_national = c(
  TRUE, TRUE,
  TRUE, TRUE
)
hhs_start_date = as.Date("2020-08-01")

>>>>

```{r hospitalization_time_trends_national, fig.cap="National trends, from April 2020 to April 2021, of HHS confirmed COVID-19 hospital admissions, plus three other signals in the COVIDcast API. Here, the HHS data has been limited to values from 2020-08-01 onward due to changes in reporting behavior, and processed into a 7-day trailing average rate per 100,000 resident population using Census Bureau estimates for 2019. HSP-Hosp is the percentage of new hospital admissions with COVID-associated diagnoses, based on claims data from health system partners, smoothed in time and adjusted for systematic day-of-week effects. Auxiliary signals have been scaled to have the same maximum value as the HHS data."}
start_day = "2020-04-15"
end_day = "2021-04-15"
as_of_day = "2021-06-01"

HOSP_SOURCES <-
  c("hhs", "hospital-admissions", "jhu-csse", "chng")
HOSP_SIGNALS <-
  c("confirmed_admissions_covid_1d",
    "smoothed_adj_covid19_from_claims",
    "confirmed_7dav_incidence_prop",
    "smoothed_adj_outpatient_covid")
hosp_names = c(
  "Hospitalizations", "HSP-Hosp",
  "Cases", "CHNG-COVID"
)
hosp_signal_has_national = c(
  TRUE, TRUE,
  TRUE, TRUE
)
hhs_start_date = as.Date("2020-08-01")
